### 2014-10-30 Abstract.tex
put back the old stuff in abstract and intro as comment
stuff

We present a new framework for modular verification of hardware designs
in the style of the Bluespec language.  That is, we formalize the idea of
components in a hardware design, with well-defined input and output channels;
and we show how to specify and verify components individually, with
machine-checked proofs in the Coq proof assistant.  In doing so, we import
to the world of hardware those modular reasoning principles that are
well-known in software verification.  As a demonstration, we verify a
fairly realistic implementation of a multicore shared-memory system.  The
main modularity split is between a memory-system component and a processor
component.  Both include nontrivial optimizations, with the memory system
employing an arbitrary hierarchy of cache nodes that communicate with each
other concurrently, and with the processor doing speculative execution of
many concurrent read operations.  Nonetheless, we prove that the combined
system implements sequential consistency.  One interesting aspect of the proof
is that the memory component is well-specified to be reused for systems
implementing a variety of weak memory models.  To our knowledge, our proof
of that memory system is the first machine verification of a cache-coherence
protocol parameterized over an arbitrary cache hierarchy, and our full-system
proof is the first machine verification of sequential consistency for a
multicore hardware design that includes memory and processors.

>>>>

\xxx{\textbf{Murali's version in red:} We provide a framework for modular verification of multi-processor hardware
systems with respect to memory model specification. In this framework, we make
use of a key observation that eventhough different memory models have different
overall system behaviors, they all share a coherent cache hierarchy. We prove
that this coherent cache hierarchy implements the \emph{store atomicity}
property, which makes it behave like an atomic instantaneous memory with
respect to the rest of the system. We further modularize the proof by defining
what is meant for a processor to be correct independently of the memory system.
As a concrete instance of our framework, we walk through a modular proof of
high-performance multi-processor implementation of Lamport's Sequential
Consistency model. The processors employ \emph{speculative execution} to
generate many concurrent loads to the memory sub-system, while obeying our
correctness criteria. We offer the first formal proof that when an atomic
memory is connected to $n$ speculative processors, the system as a whole is
sequentially consistent.  Additionally, the cache-coherent memory we present in
this paper is the first fully verified system that supports arbitrary cache
hierarchies. Our framework involves describing all our components using labeled
transition systems and we machine-verify all our proofs using the Coq proof
assistant.}
We present a new framework for modular verification of hardware designs
in the style of the Bluespec language.  That is, we formalize the idea of
components in a hardware design, with well-defined input and output channels;
and we show how to specify and verify components individually, with
machine-checked proofs in the Coq proof assistant.  In doing so, we import
to the world of hardware those modular reasoning principles that are
well-known in software verification.  As a demonstration, we verify a
fairly realistic implementation of a multicore shared-memory system.  The
main modularity split is between a memory-system component and a processor
component.  Both include nontrivial optimizations, with the memory system
employing an arbitrary hierarchy of cache nodes that communicate with each
other concurrently, and with the processor doing speculative execution of
many concurrent read operations.  Nonetheless, we prove that the combined
system implements sequential consistency.  One interesting aspect of the proof
is that the memory component is well-specified to be reused for systems
implementing a variety of weak memory models.  To our knowledge, our proof
of that memory system is the first machine verification of a cache-coherence
protocol parameterized over an arbitrary cache hierarchy, and our full-system
proof is the first machine verification of sequential consistency for a
multicore hardware design that includes memory and processors.

### 2014-10-30 Introduction.tex
put back the old stuff in abstract and intro as comment
stuff

Modularity has long been understood as a key property for effective design and
verification of such complex systems. For the designer, it allows a separation
of concerns, increasing robustness by allowing the behavior encapsulated by a
modular boundary to be realized by multiple implementations, any of which may be
dropped into the system safely. It also allows a greater measure of
parallelization of human design effort, improving development time. Similarly, verification is
simplified, as modular interface agreements provide a natural lemma structure.
This leads us towards a decomposition of the whole system verification
task into lemmas of subsystems, which can be composed in a black-box manner to
produce full-system theorems.

>>>>

Modularity has long been understood as a key property for effective design and
verification of such complex systems. For the designer, it allows a separation
of concerns, increasing robustness by allowing the behavior encapsulated by a
modular boundary to be realized by multiple implementations, any of which may be
dropped into the system safely. It also allows a greater
parallelization of human design effort, improving development time. Similarly, verification is
simplified, as modular interface agreements provide a natural lemma structure.
This leads us towards a decomposition of the whole system verification
task into lemmas of subsystems, which can be composed in a black-box manner to
produce full-system theorems.

\xxx{\textbf{Murali's version in red} This works introduces an interface enabling true modular implementation and
verification of shared memory systems. We want our modular system to permit
\emph{black-box refinement}, that is, nothing beyond the interface contract can
be assumed about other modules.  That is, we should be able to describe a
modular decomposition where we may replace either the processor nodes, the
memory with locally verified alternatives without changing the correctness of
our whole system.  To this end, we identify a key property called \emph{store
atomicity} shared by the memory component of every memory model. This property
effectively restricts the behavior of the memory sub-system to that of an
\emph{atomic instantaneous memory}. We prove that this property is in fact what
is guaranteed using the cache coherence protocols in a multi-processor system
containing a hierarchy of caches, enabling replacement of the cache hierarchy
with an atomic instantaneous memory. Similarly, on the processor side, we
define what is meant to be a correct single processor. These invariants about
the processor and the memory sub-system remains constant across memory models.
We show a concrete instance of this framework by proving that a highly
speculative multi-processor system connected to a coherent cache hierarchy
implements the sequential consistency memory model.}
